Pilot study APEROL: questionnaire data

### 2021-01-28 paper_1/paper_1.Rmd
update manuscript

# converting numbers to numeric
raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M experience" = round(mean(experience), 2),
            "min experience" = min(experience),
            "max experience" = max(experience),
            "SD experience" = round(sd(experience), 2),
            ) %>%

>>>>

# converting numbers to numeric
quest.raw.data <- quest.raw.data %>% mutate(experience = as.numeric(as.character(factor(experience))))

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "SD age" = round(sd(age), 2),
            "M experience" = round(mean(experience), 2),
            "min experience" = min(experience),
            "max experience" = max(experience),
            "SD experience" = round(sd(experience), 2))

### 2021-01-28 paper_1/paper_1.tex
update manuscript

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017). Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff et al., 2017)

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff et al., 2017). For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017). Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010). Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).

@@

\begin{tabular}{lllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{*M* age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
\bottomrule
\end{tabular}

>>>>

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017). Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff, Jarodzka, \& Boshuizen, 2017)

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff, Jarodzka, \& Boshuizen, 2017). For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017). Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010). Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).

@@

\begin{tabular}{lllllllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M experience} & \multicolumn{1}{c}{min experience} & \multicolumn{1}{c}{max experience} & \multicolumn{1}{c}{SD experience}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
\bottomrule
\end{tabular}

### 2021-01-28 paper_1/paper_1_supplement.Rmd
update manuscript

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

```{r demographicspilot1table,,echo=FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behing it
# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
# the fig.cap = then calls the text from the line just above
# fig.align allows to position the pic on page, center ist probablby best
# echo = false ensures that the code chunk does not occur in the pdf
# Now, go and try putting your own images in the paper 
#
# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/

@@

(1) classroom management
(2) positive climate and motivation
(3) clarity and structuredness
(4) activation and support
(5) presence: posture and gaze
(6) presence: voice
(7) presence: verbal and non-verbal intervention
(8) turn taking
(9) natural behaviour

@@

```{r table all sclaes, echo=FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

@@

@@

>>>>

floatsintext      : yes
figsintext        : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::word_document2 #papaja::apa6_pdf #
---

@@

```{r analysis-preferences, echo = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

```{r demographicspilottable, echo = FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

@@

# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behind it
# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
# the fig.cap = then calls the text from the line just above
# fig.align allows to position the pic on page, center ist probablby best
# echo = false ensures that the code chunk does not occur in the pdf
# Now, go and try putting your own images in the paper 
#
# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/

@@

(1) classroom management
(2) positive climate and motivation
(3) clarity and structuredness
(4) activation and support
(5) presence: posture and gaze
(6) presence: voice
(7) presence: verbal and non-verbal intervention
(8) natural behaviour

@@

```{r table all scales, echo = FALSE}

# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

@@

# to compare both sessions filter only Identical items
quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
                                                 paste(c("km_mitbekommen",
                                                         "km_klar",
                                                         "km_ungestört",
                                                         "km_aktiv",
                                                         "lkm_freundlich",
                                                         "lkm_interesse",
                                                         "lkm_kritik",
                                                         "lkm_ausreden",
                                                         "lkm_überlegen",
                                                         "lkm_rückmeldungen",
                                                         "ks_funktion",
                                                         "ks_verständlich",
                                                         "ks_sichtbar",
                                                         "af_beiträge",
                                                         "af_wechselseitig",
                                                         "af_nachdenken",
                                                         "phb_stand",
                                                         "phb_augen",
                                                         "phb_blick",
                                                         "phb_vorsichgeht",
                                                         "phb_raum",
                                                         "phb_gestik",
                                                         "phb_alleangesehen",
                                                         "ps_deutlich",
                                                         "ps_klar",
                                                         "ps_impulse",
                                                         "pi_nonverbal",
                                                         "pi_zubewegen",
                                                         "pi_direkt",
                                                         "m_natürlich",
                                                         "m_fiktiv",
                                                         "m_verhalten"),
                                                    collapse = '|')))

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))

@@

# remove duplicate labels from the table column "group" to create the APA-style omission of categorical variables
# this is easier than the stub_indent option in apa_table
scale.quest.table$group[duplicated(scale.quest.table$group)] <- ""

@@

In addition, we plotted all scales for experts and novices. Graph provides boxplots and individual data for both groups.

```{r boxplot scales, echo = FALSE}
# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
                                                 paste(c("km_mitbekommen",
                                                         "km_klar",
                                                         "km_ungestört",
                                                         "km_aktiv",
                                                         "lkm_freundlich",
                                                         "lkm_interesse",
                                                         "lkm_kritik",
                                                         "lkm_ausreden",
                                                         "lkm_überlegen",
                                                         "lkm_rückmeldungen",
                                                         "ks_funktion",
                                                         "ks_verständlich",
                                                         "ks_sichtbar",
                                                         "af_beiträge",
                                                         "af_wechselseitig",
                                                         "af_nachdenken",
                                                         "phb_stand",
                                                         "phb_augen",
                                                         "phb_blick",
                                                         "phb_vorsichgeht",
                                                         "phb_raum",
                                                         "phb_gestik",
                                                         "phb_alleangesehen",
                                                         "ps_deutlich",
                                                         "ps_klar",
                                                         "ps_impulse",
                                                         "pi_nonverbal",
                                                         "pi_zubewegen",
                                                         "pi_direkt",
                                                         "m_natürlich",
                                                         "m_fiktiv",
                                                         "m_verhalten"),
                                                    collapse = '|')))

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))

quest.plot <- quest.raw.data %>%
  ggplot( aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
# quest.plot

(ref:boxplot_all_scales-caption) Boxplot with individual points for all scales

```{r boxplot_all_scales, fig.cap = "(ref:boxplot_all_scales-caption)", fig.align = "center", echo = FALSE}

knitr::include_graphics("./pictures/boxplot_all_scales.png", dpi = 108)

In addition, we evaluated the duration of the speaking time during the lesson in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices.

```{r duration speaking time, echo = FALSE}
# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))
view(quest.raw.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))

speaking.plot <- quest.raw.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot

### 2021-01-28 paper_1/paper_1_supplement.tex
update manuscript

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\caption{\label{tab:demographicspilot1table,}Demographic Informationand and Teaching Experience}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  classroom management
\item
  positive climate and motivation
\item
  clarity and structuredness
\item
  activation and support
\item
  presence: posture and gaze
\item
  presence: voice
\item
  presence: verbal and non-verbal intervention
\item
  turn taking
\item
  natural behaviour
\end{enumerate}

@@

\begin{verbatim}
## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA
\end{verbatim}

\begin{verbatim}
## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt

## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt

## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt
\end{verbatim}

@@

\caption{\label{tab:table all sclaes}Mean values of all scales}

@@

\begin{tabular}{llllll}
\toprule
group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
\midrule
expert & Aktivierung und Förderung & NA & 1 & 4 & 1.11\\
expert & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.89\\
expert & Klassenmanagement & NA & 1 & 4 & 0.80\\
expert & Lernförderliches Klima und Motivierung & NA & 2 & 4 & 0.62\\
expert & Manipulationsitem & NA & 2 & 4 & 0.69\\
expert & Manipulationsitem & NA & 3 & 4 & 0.52\\
expert & Präsenz/Haltung\_Blick & NA & 1 & 4 & 0.92\\
expert & Präsenz/Stimme & NA & 1 & 4 & 1.16\\
expert & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.63\\
expert & Präsenz/verbale\_nonberbale Intervention & NA & 2 & 4 & 0.78\\
expert & Redeanteil & NA & 60 & 95 & 10.53\\
novice & Aktivierung und Förderung & NA & - & 4 & NA\\
novice & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.87\\
novice & Klassenmanagement & NA & 0 & 4 & 0.91\\
novice & Lernförderliches Klima und Motivierung & NA & 0 & 4 & 0.90\\
novice & Manipulationsitem & NA & 2 & 4 & 0.45\\
novice & Manipulationsitem & NA & 2 & 4 & 0.75\\
novice & Nachdenkzeit & NA & - & 5-10 & NA\\
novice & Präsenz/Haltung\_Blick & NA & 0 & 4 & 0.95\\
novice & Präsenz/Stimme & NA & 0 & 4 & 1.04\\
novice & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.69\\
novice & Präsenz/verbale\_nonberbale Intervention & NA & 1 & 4 & 0.91\\
novice & Redeanteil & NA & 50 & 95 & 12.97\\
novice & Störung & NA & - & Stift auf Papier schreiben & NA\\
\bottomrule
\end{tabular}

@@

>>>>

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  classroom management
\item
  positive climate and motivation
\item
  clarity and structuredness
\item
  activation and support
\item
  presence: posture and gaze
\item
  presence: voice
\item
  presence: verbal and non-verbal intervention
\item
  natural behaviour
\end{enumerate}

@@

@@

\caption{\label{tab:table all scales}Mean values of all scales}

@@

\begin{tabular}{llllll}
\toprule
group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
\midrule
expert & Activation and support & 3.33 & 2.00 & 4.00 & 0.80\\
 & Clarity and structuredness & 3.70 & 1.00 & 4.00 & 0.73\\
 & Classroom management & 3.23 & 1.00 & 4.00 & 0.90\\
 & Natural behaviour & 3.57 & 2.00 & 4.00 & 0.63\\
 & Positive climate and motivation & 3.60 & 2.00 & 4.00 & 0.62\\
 & Presence: posture/gaze & 3.29 & 1.00 & 4.00 & 0.92\\
 & Presence: verbal and non-verbal intervention & 3.07 & 2.00 & 4.00 & 0.78\\
 & Presence: voice & 3.57 & 2.00 & 4.00 & 0.63\\
novice & Activation and support & 2.23 & 0.00 & 4.00 & 1.39\\
 & Clarity and structuredness & 3.35 & 1.00 & 4.00 & 0.76\\
 & Classroom management & 2.82 & 1.00 & 4.00 & 0.90\\
 & Natural behaviour & 3.13 & 2.00 & 4.00 & 0.71\\
 & Positive climate and motivation & 3.11 & 0.00 & 4.00 & 0.90\\
 & Presence: posture/gaze & 2.95 & 0.00 & 4.00 & 0.95\\
 & Presence: verbal and non-verbal intervention & 2.88 & 1.00 & 4.00 & 0.97\\
 & Presence: voice & 3.30 & 2.00 & 4.00 & 0.74\\
\bottomrule
\end{tabular}

@@

\clearpage
\renewcommand{\listfigurename}{Figure captions}

\clearpage
\renewcommand{\listtablename}{Table captions}

### 2021-01-28 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update manuscript

# filter by parameter variable, i.e. create a subset for presence: posture and gaze
phb.data <- raw.data %>% filter(scale == "Präsenz/Haltung_Blick")

@@

names(phb.plot.sd)

@@

# create a table of all scales 
raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2),
            ) %>% 
  knitr::kable(digits = 2)

>>>>

# filter by parameter variable, i.e. create a subset for presence: posture and gaze
phb.data <- raw.data %>% filter(scale == "Presence: posture/gaze")

@@

@@

# create a table of all scales 
table.scales <- raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2),
            ) %>% 
  knitr::kable(digits = 2)
